---
title: "Team BD5 - Final Project"
author: "Samuel Buxton, Moses Chong, Tom Truong, Will Park, ZubairAhmed Amjad"
date: "May 30, 2018"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Summary 

## Purpose

The purpose of this project is to provide **political campaign staff** with information regarding **politicans** and how they are viewed by the public through _keywords used on Twitter_. They can use this information to see what _words are associated with particular politicians_, so they can set **election strategies** and **target their voters accordingly**.

## Source of the Data

We used the [_Twitter API's_](https://developer.twitter.com/en.html)
[**Search Tweets**](https://developer.twitter.com/en/docs/tweets/search/api-reference/get-search-tweets.html)
feature with the assistance of the
[**TwitteR** package](https://cran.r-project.org/web/packages/twitteR/twitteR.pdf)
to make things easier to code.

## About the Topic



## About our Code

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



