---
title: "Team BD5 - Final Project"
author: "Samuel Buxton, Moses Chong, Tom Truong, Will Park, ZubairAhmed Amjad"
date: "May 30, 2018"
output:
  html_document:
    css: ./www/style.css
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Summary 

## Purpose

The purpose of this project is to provide **political campaign staff** with
information regarding **politicans** and how they are viewed by the public
through _keywords used on Twitter_. They can use this information to see what
_words are associated with particular politicians_, so they can set
**election strategies** and **target their voters accordingly**.

## Source of the Data

We used the [_Twitter API's_](https://developer.twitter.com/en.html)
[**Search Tweets**](https://developer.twitter.com/en/docs/tweets/search/api-reference/get-search-tweets.html)
feature with the assistance of the
[**TwitteR** package](https://cran.r-project.org/web/packages/twitteR/twitteR.pdf)
to extract data from **Twitter**.

## About the Topic

Inspired by the _chaos caused by politics and the internet_ in recent times, we
decided to make this application to revolve around **figuring out how certain
politicians are viewed by the public eye**.
_What wouldn't be better by searching about them through Tweets?_    

Even though our project allows anything to be input as a hashtag search on
Twitter, for the sake of our **Final Project** political related search terms is
only appropriate. Our project features:  
- **A Sample of 100 Tweets/Retweets by Term**  
- **_"Sentiment Values" (positive to negative)_ on Tweets by Term and
Retweet Count**  
- **The Top 5 Tweets/Retweets based on popularity by Term**  
- **A _Word Cloud_ that takes a Term and makes the _most associated words_ into
a cloud like shape**


## About our Code

We used quite a few custom packages to make this project easier than it looks.
Besides the main
[**TwitteR** package](https://cran.r-project.org/web/packages/twitteR/twitteR.pdf),
we used:  
- [**tidytext**](https://cran.r-project.org/web/packages/tidytext/tidytext.pdf)
_(to help Text Mine using `dplyr` and `ggplot2`)_  
- [**ggpubr**](https://cran.r-project.org/web/packages/ggpubr/ggpubr.pdf)
_(to help customize our `ggplot2` plots)_  
- [**tm**](https://cran.r-project.org/web/packages/tm/tm.pdf)
_(to help Text Mine through tweet corpuses)_  
- [**sentimentr**](https://cran.r-project.org/web/packages/sentimentr/sentimentr.pdf)
_(to help determine the sentiment towards certain words)_  
- [**wordcloud**](https://cran.r-project.org/web/packages/wordcloud/wordcloud.pdf)
_(to help make the word cloud visualization)_  

```{r, echo = FALSE, message = FALSE}
library(shiny)
library(plotly)
library(tidytext)
library(ggpubr)
library(httr)
library(jsonlite)
library(dplyr)
library(ggplot2)
library(twitteR)
library(RCurl)
library(tm)
library(wordcloud)

source("api-keys.R")
source("./scripts/key_terms.R")

setup_twitter_oauth(consumer_public, consumer_private, public_key, private_key)

shinyApp(
  ui <- shinyUI(
  navbarPage(
    theme = "./www/style.css",
    "Final Project",
    tabPanel(
      "Sample by Term",
      titlePanel("Sample 100 Tweets/Retweets by Term"),
      sidebarLayout(
        sidebarPanel(
          textInput("term",
            label = "Search for a Term",
            value = "Trump"
          )
        ),
        mainPanel(
          tableOutput("key_tweets")
        )
      )
    ),
    tabPanel(
      "HashTag",
      titlePanel("HashTag"),
      sidebarLayout(
        sidebarPanel(
          width = 3,
          textInput("hashtag",
            label = "Search for a Term",
            value = "Trump"
          )
        ),
        mainPanel(
          plotOutput("plot"),
          plotOutput("plot2")
        )
      )
    ),
    tabPanel(
      "Most Retweeted",
      titlePanel("Top 5 Tweets/Retweets by Retweets"),
      sidebarLayout(
        sidebarPanel(
          textInput("top_5",
            label = "Top 5 Tweets/Retweets from a Random Sample",
            value = "Trump"
          ),
          sliderInput("quantity",
            label = "Select of Sample Size",
            min = 1,
            max = 1000,
            value = 500,
            ticks = TRUE,
            animate = FALSE
          )
        ),
        mainPanel(
          plotlyOutput("tweets_plot"),
          tableOutput("tweets_tbl")
        )
      )
    ),
    tabPanel(
      "Word Cloud",
      titlePanel("Trends in Words That are Used Most Commonly in Relation
                 to a Politician"),
      sidebarLayout(
        sidebarPanel(
          width = 2,
          textInput("Politician",
            label = "Enter Politician Name",
            value = "Trump"
          ),
          sliderInput("Number", "Select Number of Tweets",
            min = 50, max = 500, value = 275
          ),
          radioButtons("lang", "Select Language", c(
            "English" = "en",
            "Spanish" = "es"
          )),
          submitButton(text = "Run")
        ),
        mainPanel(
          plotOutput("pol_wordcloud", width = "1500px", height = "1000px")
        )
      )
    )
  )
),

  server <- function(input, output) {
    output$key_tweets <- renderTable({
      return(term_search(input$term))
    })
    tweets <- reactive({
      popular <- return(term_top_5(input$top_5, input$quantity))
    })
    output$tweets_plot <- renderPlotly({
      return(plot_tweets(tweets()))
    })
    output$tweets_tbl <- renderTable({
      tweets()[, c("Twitter Handle", "Tweet", "Number of Retweets")]
    })

    output$plot <- renderPlot({
      tweet_info <- searchTwitter(paste0("#", input$hashtag), 50)
      tweet_info_df <- twListToDF(tweet_info)

      text <- data_frame(tweet = tweet_info_df$text) %>%
        unnest_tokens(word, tweet)

      tweet_score <- text %>%
        inner_join(get_sentiments("afinn"), by = "word") %>%
        count(word, score, sort = TRUE) %>%
        ungroup()

      # I split these up for clarity, although they could be combined
      tweet_sentiment <- text %>%
        inner_join(get_sentiments("nrc"), by = "word") %>%
        count(sentiment, sort = TRUE) %>%
        ungroup() %>%
        rename(word = sentiment)

      binary_sentiment <- tweet_sentiment %>%
        inner_join(get_sentiments("bing"), by = "word") %>%
        ungroup() %>%
        arrange(n)


   is.data.frame(binary_sentiment)
      total_score <- tweet_score$score * tweet_score$n

      # I would like to point out that it was NOT easy to get those colors right
      positivity_plot <- ggplot(data = tweet_score, aes(x = factor(word),
                                                        y = total_score)) +
        geom_bar(aes(fill = total_score < 0), stat = "identity") +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        scale_fill_manual(guide = FALSE, breaks = c(TRUE, FALSE),
                          values = c("green", "red")) +
        labs(
          x = "Most Common Words in Tweets",
          y = "Positivity Score",
          title = "Positivity of Tweets",
          fill = "Positivity"
        )

      # Using only 3 through 8 since 'positive' and 'negative are by
      # far the most popular sentiments, although they cannot be used

      sentiment <- ggplot(binary_sentiment, aes(x = factor(word,
                                              levels = unique(word)), y = n)) +
        geom_bar(stat = "identity", aes(fill = factor(sentiment))) +
        coord_flip() +
        labs(
          x = "Most Common Emotions",
          y = "Frequency",
          title = "Emotions Conveyed by Tweets",
          fill = "Positivity"
        )

      ggarrange(sentiment, positivity_plot,
        labels = c("A", "B"),
        ncol = 2, nrow = 1
      )
    })

    output$plot2 <- renderPlot({
      search <- searchTwitter(input$hashtag)
      popular_tweets <- twListToDF(search)
      bar_stuff <- popular_tweets %>%
        select(screenName, retweetCount)

      bar_plot <- ggplot(bar_stuff, aes(screenName, retweetCount))
      bar_plot + geom_bar(stat = "identity", fill = "#FF6666") +
        xlab("Usernames") +
        ylab("Retweet Count") +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
    })

    output$pol_wordcloud <- renderPlot({
      sample_tweets <- searchTwitter(input$Politician,
                                     lang = input$lang,
                                     n = input$Number,
                                     resultType = "recent"
      )
      Sample_tweets_text <- sapply(sample_tweets, function(x) x$getText())
      Sample_tweets_text2 <- iconv(
        Sample_tweets_text, "latin1",
        "ASCII//TRANSLIT"
      )
      Sample_tweets_text3 <- iconv(Sample_tweets_text2, to = "ASCII//TRANSLIT")
      Sample_tweets_corpus <- Corpus(VectorSource(Sample_tweets_text3))
      Sample_tweets_corpus <- tm_map(Sample_tweets_corpus, tolower)
      Sample_tweets_corpus <- tm_map(Sample_tweets_corpus, removePunctuation)
      Sample_tweets_corpus <- tm_map(
        Sample_tweets_corpus, removeWords,
        stopwords(input$lang)
      )
      Sample_tweets_corpus <- tm_map(Sample_tweets_corpus, stripWhitespace)

      # Filter commonly used words for more accurate representation
      Sample_tweets_corpus <- tm_map(
        Sample_tweets_corpus, removeWords,
        c(
          "trump", "donald", "president", "america",
          "hillary", "americans", "think", "says",
          "call", "know", "will", "claimed", "even",
          "every", "amp", "said", "voted", "rt",
          "realdonaldtrump", "therealroseanne",
          "now", "made", "let", "like", "just",
          "yesterday", "makes", "knows", "someone",
          "called", "comments", "got", "one", "many",
          "knew", "knows"
        )
      )
      pal2 <- brewer.pal(8, "Dark2")
      wordcloud(Sample_tweets_corpus,
                random.order = FALSE,
                colors = pal2
      )
    })
  },
  
  options = list(height = 1000)
)
```
